### 2023-03-06 paper/main.tex
updated paper

\documentclass[letterpaper, 10 pt, conference]{ieeeconf} 
\IEEEoverridecommandlockouts                              
\overrideIEEEmargins

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{graphicx}

@@

\input{titlepage}
%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\end{abstract}

@@

\section{Problem Definition}
\subsection{outline the problem requirements and include the ap- plication domain and motivations of your project (1 page).}
Develop a software that facilitates administration of surveys and feedback collection. The software must be fast, robust, and friendly.

Marketing/Business Operations

Businesses want meaningful direct feedback on their products and services. Our project aims to provide a generalized solution to context-specific customer feedback monitoring without the need of onsite hardware to capture responses. In other terms, our app is a solution for conducting self-administered surveys.

@@

\section{Application Benefits}
\subsection{what are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}

\section{Requirements Elicitation and Specification}
\subsection{Functional requirements list (only the ones that you have imple- mented) for each user role (two exactly). Name each requirement and explain it briefly.}
\subsection{For each user role, provide the use case diagram with all the use cases and actors.}
\subsection{Describe in detail two use cases using the activity diagram. Choose the most complex use cases.}
\subsection{Software qualities: Correctness, Time-eﬀiciency and Robustness. In- clude at least two concrete examples for each quality for each user role. The sign-in and sign-up use cases are excluded from the examples.
}

@@

\section{Top-level and Low-level Software Design}
\subsection{Provide the MVC architecture according to the selected Web frame- work. Also, describe at least three benefits of MVC for your application.}
\subsection{Observer and Factory design patterns. Explain in detail the usability of these two patterns for your specific application. Include the complete class diagram for each pattern. Also provide the algorithms corresponding to the pattern’s important methods. For each class, provide the data types of the attributes and prototypes of the methods.}
\subsection{Provide the class diagram of the whole system by incorporating the two design patterns.
}

@@

\section{Conclusion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}

Appendixes should appear before the acknowledgment.

@@

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

>>>>

\documentclass[letterpaper, 12 pt, conference]{ieeeconf} 
\IEEEoverridecommandlockouts                              
\overrideIEEEmargins
\usepackage{setspace}

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{graphicx}

@@

\input{titlepage}

@@

\doublespacing 
\onecolumn

\section{Problem Definition}
\subsection{outline the problem requirements and include the application domain and motivations of your project (1 page).}

Business and product owners want meaningful feedback from their customers to assist in their growth and success. It can be difficult to collect this information without onsite hardware and processing the data provided can be a timely task. As with many forms of customer engagement and ratings, customers can be unwilling to participate in traditional methods of feedback if too many steps are required, so the data collected will not be an accurate portrayal of opinions.

In order to solve this problem, we have created a web application that allows for customers to provide their feedback in a simplistic way, and displays this information for businesses or owners in a way that it simple to understand without the need for onsite hardware. By allowing the customer to interact with a site that is not cumbersome, and can be done from the convenience of their smart phone, many more customers will be willing to submit their thoughts and opinions.

\newpage    
\section{Application Benefits}
\subsection{what are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}

@@

\textbf{discuss survey monkey differences}

\textbf{discuss questionpro differences}

\newpage
\section{Requirements Elicitation and Specification}
\subsection{Functional requirements list (only the ones that you have implemented) for each user role (two exactly). Name each requirement and explain it briefly.}
\subsection{For each user role, provide the use case diagram with all the use cases and actors.}
\subsection{Describe in detail two use cases using the activity diagram. Choose the most complex use cases.}
\subsection{Software qualities: Correctness, Time-eﬀiciency and Robustness. In- clude at least two concrete examples for each quality for each user role. The sign-in and sign-up use cases are excluded from the examples.
}

@@

\section{Top-level and Low-level Software Design}
\subsection{Provide the MVC architecture according to the selected Web frame- work. Also, describe at least three benefits of MVC for your application.}
\subsection{Observer and Factory design patterns. Explain in detail the usability of these two patterns for your specific application. Include the complete class diagram for each pattern. Also provide the algorithms corresponding to the pattern’s important methods. For each class, provide the data types of the attributes and prototypes of the methods.}
\subsection{Provide the class diagram of the whole system by incorporating the two design patterns.}

@@

@@

@@

\newpage
